Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-09-16 paper/case-study.tex
Add text regarding who adds requirements and remove redundancy.

In this section, we outline the application of the BriefCASE tool towards the development of a UAV surveillance system as a part of the DARPA CASE program.
The motivation was to showcase the utility and capability of the BriefCASE toolchain on an industrial scale problem, to determine whether the technology provides engineers with early validation of their model; produces early information about cyber-vulnerabilities; provides effective mitigations; and handles a complex real-world message format, namely  the UxAS message format.

@@

Within the software model, we have formalized some of the high-level requirements as assume-guarantee contracts.  We perform a formal analysis using the AGREE tool (which is integrated with the BriefCASE environment) to verify that the model satisfies the contracts.  For the initial version of our design, the verification passes.
%
Although we are satisfied with the results of the formal verification using AGREE, we have not yet analyzed the design for cyber-vulnerabilities.  
In BriefCASE, we analyze the model using one (or more) of the integrated cybersecurity analysis tools.  The tools generate a list of new requirements corresponding to cyber vulnerabilities found in the design,
and we need to satisfy these requirements by modifying the design.
%  To satisfy these requirements we need to mitigate the vulnerabilities discovered by the analysis by modifying the design.
%
For example, because we annotated the open-source UxAS component as \texttt{uncontrolled} (colored red in \figref{fig:sw-initial}), the cyber analysis tools generate requirements for ensuring that unverified or malicious code (which could potentially be embedded in the component) will not impact other processes.

In total, seven cyber requirements are generated and imported into our model.  These include four \textit{wellformedness} requirements, two requirements for \textit{monitoring} the behavior of the open-source UxAS component, and an \textit{attestation} requirement for ensuring the Ground Station software has not been tampered with.  Requirements are imported into the model as goals in a Resolute assurance case.  Because we can run Resolute at any time during development, we can easily determine for a given snapshot of the model which requirements are not yet supported by evidence.

@@

The filter behavior for each component is specified in AGREE.  This enables formal verification within the modeling environment, and also provides a means for synthesizing the component implementation in a provably correct manner using the SPLAT tool.  Because SPLAT is integrated with BriefCASE, the proof it emits when synthesizing component code is used as evidence in the Resolute goal for the corresponding mitigation.  When Resolute evaluates whether such a goal is supported by evidence, it checks for the existence of the synthesis proof in addition to verifying that the architecture is correct.

The AGREE filter policies for the four UxAS connections are similar, and check that record values contained in the messages are within appropriate ranges.  For example, the Automation Response message filter, which drops messages containing malformed flight plans, is defined as shown in \figref{fig:automation-response-filter}.  Although \texttt{Latitude}, \texttt{Longitude} and \texttt{Altitude} are defined as 64-bit floating-point values, the filter only passes messages containing waypoint values between [-90,90], [-180,180], and [0,15000], respectively.

@@

In addition to monitoring the UxAS output for malformed messages, we must also monitor for suspicious behavior.  This requires adding components for detecting that UxAS has crashed, as well as monitoring the correctness of the flight plans it produces.  The Monitor transform is applied for this class of mitigation.  In general, monitors observe a channel and compare its contents against a reference signal or constant.  The monitor policy specifies acceptable comparisons, and if violated, the monitor sends out an alert.  A monitor can choose to \textit{gate} the observed signal, in which case it also acts as a special kind of filter and drops the message if the policy is violated.  The \textit{monitoring} requirements drive two transforms.  The first adds a \textit{response} monitor to send an alert if UxAS does not emit a response within a set amount of time from receiving a request.  The second adds a \textit{geofence} monitor to ensure that generated flight plans are compliant with the specified keep-in and keep-out zones.  The Geofence Monitor is a gated monitor; it prevents the observed Automation Response message from reaching the Waypoint Manager. 
%
Similar to the filters, the monitor policies are specified in AGREE. For example, 
%The Response Monitor specification is shown in \figref{fig:response-monitor}, and 
the Geofence Monitor specification is shown in \figref{fig:geofence-monitor}.

@@

So far, we have addressed requirements that 
%The requirements that have been addressed so far
mitigate vulnerabilities related to malformed messages and malicious behavior \textit{on-board} the UAV.  But we also want to protect against a compromised Ground Station transmitting wellformed, but malicious commands. The final cyber requirement is mitigated by the Attestation transform~\cite{attestation-copland} that adds two components to the UAV software: an Attestation Manager for evaluating remote systems like the Ground Station, and an Attestation Gate for filtering messages from sources that have not been approved by the Attestation Manager.  The Attestation Manager is implemented in CakeML and automatically inserted into the application code base by BriefCASE.  Because the Attestation Gate acts as a filter, the transform automatically generates its complete AGREE specification.%, as shown in \figref{fig:attestation}.

% \begin{figure}[h]
% 	\centering
% 	\includegraphics[width=1\columnwidth]{figs/attestation.png}
% 	\caption{Atestation specification.} 
% 	\label{fig:attestation} 
% \end{figure}

After transforming the model to address the cyber requirements, the software architecture now appears as shown in \figref{fig:hardened-sw}.  The components in green were added to the model by way of an automated BriefCASE transform and are critical for mitigating cyber attacks. 
We formally verify the model with AGREE to show that all of the component contracts are satisfied, including the new contracts introduced during the model transformations.
Because it is imperative that these high-assurance component implementations are correct,
we run the SPLAT tool to produce provably-correct code.  
The synthesized code is output to a directory in the build file system with the location specified for each component in the model.  The corresponding correctness proof is used in our assurance case as additional evidence that the vulnerability has been properly mitigated.

@@

Once we have determined that the model is correct and satisfies its cyber requirements, and the software components in the model have been implemented, either by SPLAT or other means, the system can be built and deployed.  We run the HAMR tool to generate the component stubs and infrastructure code necessary to enable component communication and execution according to a specified schedule.
HAMR translates the AADL system model to code that implements threading infrastructure and inter-component communication consistent with the AADL computational model.
%
HAMR then compiles the software to execute on seL4~\cite{sel4-2009}, a verified capability-based microkernel (accompanied by formal proof of spatial isolation properties down to the binary level).

The UAV and Ground Station software were deployed on ODROID XU4 hardware, and communicated with each other over ethernet.  The AMASE flight simulator, representing the Flight Control Computer was run on a Linux machine and connected to the UAV ODROID via a serial connection.  The UxAS implementation on the UAV was modified by adding malicious code that would prevent it from responding to Automation Requests or produce flight plans that would violate the operating region constraints.  Some of the Line Search Task messages transmitted from the Ground Station contained malformed messages that would modify the UxAS behavior. In addition, we modified the Ground Station to simulate a breach for our evaluation of the attestation transform.
%
We performed a set of tests on the initial system (\figref{fig:sw-initial}) prior to applying our cyber-resiliency mitigations in order to verify the effectiveness of the malicious code.  
A third party evaluator repeated the tests on the hardened system and % were able to 
demonstrated that our mitigations were successful.
%The following scenarios were exercised (status messages from the high-assurance components in the hardened system are in \figref{fig:mitigation-output}):
The following scenarios were exercised:

>>>>

In this section, we outline the application of the \brfcs\ tool towards the development of a UAV surveillance system.
The motivation was to showcase the utility and capability of the BriefCASE toolchain on an industrial scale problem, to determine whether the technology provides designers with early validation of their model; produces early information about cyber-vulnerabilities; provides effective mitigations; and handles a complex real-world message format, namely  the UxAS message format.

@@

Within the software model, we have formalized some of the high-level requirements as assume-guarantee contracts.  We perform a formal analysis using the \agr\ to verify that the model satisfies the contracts.  For the initial version of our design, the verification passes.
%
Although we are satisfied with the results of the formal verification using AGREE, we have not yet analyzed the design for cyber-vulnerabilities.
In \brfcs, we analyze the model using one (or more) of the integrated cybersecurity analysis tools.
As the designers of the system, we reviewed the list of potential vulnerabilities, and then added new requirements to the system model.
%  To satisfy these requirements we need to mitigate the vulnerabilities discovered by the analysis by modifying the design.
%
For example, the vulnerbility analysis noted that UxAS as an open source project, so we marked that component as \texttt{uncontroled} (colored red in \figref{fig:sw-initial}) and added requirements for ensuring that unverified or malicious code (which could potentially be embedded in the component) is not able impact other components.

In total, we added seven cyber requirements from the vulnerability analysis into our model.  These include four \textit{wellformedness} requirements, two requirements for \textit{monitoring} the behavior of the open-source UxAS component, and an \textit{attestation} requirement for ensuring the Ground Station software has not been tampered with.  Requirements are imported into the model as goals in th assurance case \cite{resolute-destion}.  Because we can build the assurance case at any time during development, we can easily determine for a given snapshot of the model which requirements are not yet supported by evidence.

@@

The filter code contracts for the four UxAS connections are similar, and check that record values contained in the messages are within appropriate ranges.  For example, the Automation Response message filter, which drops messages containing malformed flight plans, is defined as shown in \figref{fig:automation-response-filter}.  Although \texttt{Latitude}, \texttt{Longitude} and \texttt{Altitude} are defined as 64-bit floating-point values, the filter only passes messages containing waypoint values between [-90,90], [-180,180], and [0,15000], respectively.

@@

In addition to monitoring the UxAS output for malformed messages, we must also monitor for suspicious behavior.  This requires adding components for detecting that UxAS has crashed, as well as monitoring the correctness of the flight plans it produces.  The Monitor transform is applied for this class of mitigation.  We add a \textit{response} monitor to send an alert if UxAS does not emit a response within a set amount of time from receiving a request.  And we add a \textit{geofence} monitor to ensure that generated flight plans are compliant with the specified keep-in and keep-out zones.  The Geofence Monitor is a gated monitor in that it prevents the observed automation response from reaching the Waypoint Manager if the zones are violated.
The Geofence Monitor specification is shown in \figref{fig:geofence-monitor}.

@@

So far, we have addressed requirements that
%The requirements that have been addressed so far
mitigate vulnerabilities related to malformed messages and malicious behavior \textit{on-board} the UAV.  But we also want to protect against a compromised ground station transmitting well-formed, but malicious, commands. The final cyber requirement is mitigated by a transform that adds two components to the UAV software: an Attestation Manager for evaluating remote systems like the Ground Station, and an Attestation Gate for filtering messages from sources that have not been approved by the Attestation Manager~\cite{attestation-copland}.  The Attestation Manager \ckml\ implementation is automatically inserted into the application code base by \brfcs. The Attestation Gate does require a code contract that is completely generated by the transform since it has a very specialized behavior as defined by the transform.

After transforming the model to address the cyber requirements, the software architecture now appears as shown in \figref{fig:hardened-sw}.  The green shaded components were added by the transform with the exception of the UxAS component. The added components are critical for mitigating cyber attacks.
After unit testing the monitors, we formally verify the model with \agr\ to show that all of the component contracts are satisfied.
We then run \splt\ to produce provably-correct code.
The synthesized code is output to a directory in the build file system with the location specified for each component in the model.  The corresponding correctness proof is used in our assurance case as additional evidence that the vulnerability has been properly mitigated.

@@

Once we have determined that the model is correct and satisfies its cyber requirements, and the software components in the model have been implemented, either by \splt\ or other means, the system can be built and deployed.  We run the HAMR tool to generate the component stubs and infrastructure code necessary to enable component communication and execution according to a specified schedule.
% HAMR translates the AADL system model to code that implements threading infrastructure and inter-component communication consistent with the AADL computational model.
%
HAMR then compiles the software to execute on seL4.

The UAV and Ground Station software were deployed on ODROID XU4 hardware, and communicated with each other over ethernet.  The AMASE flight simulator, representing the Flight Control Computer was run on a Linux machine and connected to the UAV ODROID via a serial connection.  The UxAS implementation on the UAV was modified by adding malicious code that would prevent it from responding to Automation Requests or produce flight plans that would violate the operating region constraints.  Some of the Line Search Task messages transmitted from the Ground Station contained malformed messages that would modify the UxAS behavior. In addition, we modified the Ground Station to simulate a breach for our evaluation of the attestation transform.
%
We performed a set of tests on the initial system (\figref{fig:sw-initial}) prior to applying our cyber-resiliency mitigations in order to verify the effectiveness of the malicious code.
A third party evaluator repeated the tests on the hardened system and % were able to
demonstrated that our mitigation strategy was successful.
%The following scenarios were exercised (status messages from the high-assurance components in the hardened system are in \figref{fig:mitigation-output}):
The following scenarios were exercised:
